Search with CitationGecko

### 2022-09-14 notebooks/Search_Citation_Gecko.Rmd
Formats the "Citation Gecko notebook" free text with maximum column width

---
title: "Search with CitationGecko"
output: html_notebook
bibliography: ../www/Multidimensional-parameters-MCLM.bib
csl: ../www/apa-old-doi-prefix.csl
---

@@

I create a new collumn in the Excel file "CLASSIFICATION", in column "AI", where I fill in the results of the manual classification. Then, to decide whether a paper is relevant, I search for citations of @reckase_difficulty_1985, @reckase_discriminating_1991, @ackerman_creating_1994, and @zhang_conditional_1999. If the paper mentions the computation of the multidimensional difficulty (MDIFF, MID, or MDL) or discrimination (MDISC) parameter (I search for those terms and also "difficulty" and "discrimination"), then I check whether they assume an orthogonal latent space (by searching for "distribution", "orthogonal", and "correlation", if necessary).

>>>>

---
title: "Search with CitationGecko"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
  html_notebook: default
bibliography: "../www/Multidimensional-parameters-MCLM.bib"
csl: "../www/apa-old-doi-prefix.csl"
---

@@

I create a new column in the Excel file "CLASSIFICATION", in column "AI",
where I fill in the results of the manual classification.
Then, to decide whether a paper is relevant, I search for citations of
@reckase_difficulty_1985, @reckase_discriminating_1991, @ackerman_creating_1994,
and @zhang_conditional_1999. If the paper mentions the computation of
the multidimensional difficulty (MDIFF, MID, or MDL) or discrimination (MDISC)
parameter (I search for those terms and also "difficulty" and "discrimination"),
then I check whether they assume an orthogonal latent space (by searching for
"distribution", "orthogonal", and "correlation", if necessary).
